Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2023-12-04 SEIR.tex
Updates from Overleaf

The majority of the confidence intervals contain the nominal probability (see \cref{SEIR:fig:sim-coverage}).
There is a tendency for the coverage to be slightly lower than the nominal probability, suggesting that the credible intervals are slightly too narrow; this is a common problem when using random-walk MCMC.
\todo{cite issues with random-walk MCMC exploring space}
This is similar when considering coverage of the derived quantities incidence and prevalence (see \cref{SEIR:fig:sim-inc-prev}).
\begin{figure}
    \includegraphics{SEIR/sim/coverage}
    \caption[Coverage of simulation study]{%
        Point estimate and 95\% confidence interval for coverage of the 50\%, 75\%, and 95\% central credible intervals for each parameter; see text for full definition.
        Vertical lines show the nominal coverage.
    }
    \label{SEIR:fig:sim-coverage}
\end{figure}
\begin{figure}
    \includegraphics[width=0.9\paperwidth]{SEIR/sim/predictive_coverage}
    \caption[Coverage of simulation study (derived quantities)]{%
        Point estimate and 95\% confidence interval for coverage of the 50\%, 75\%, and 95\% central credible intervals for incidence (top) and prevalence (bottom); see text for full definition.
        Horizontal lines show the nominal coverage.
    }
    \label{SEIR:fig:sim-inc-prev}
\end{figure}

@@

The 11--16 age group (roughly corresponding to compulsory secondary school education) is estimated to have the highest incidence (see \cref{SEIR:fig:incidence}).
Incidence is smooth within each week but shows discontinuities between weeks.
This is because the parameters within $\matr{\beta}(t)$ are constant within each week.
A constant $\matr{\beta}(t)$ leads to exponential growth over short time periods, once the initial dynamics have died out.
When the peak in incidence is estimated to occur varied by region, but due to this reason, is almost always on a Friday (see \cref{SEIR:fig:peak-incidence}).
\begin{figure}
    \includegraphics{SEIR/CIS/incidence}
    \caption[Posterior estimates of incidence]{%
        Posterior estimates (95\% CrI) of incidence by region and age.
        See main text for discussion.
    }
    \label{SEIR:fig:incidence}
\end{figure}

\begin{figure}
    \includegraphics{SEIR/CIS/p_peak}
    \caption[Posterior estimates of peak incidence timing]{%
        Posterior probability of the peak incidence for each region and age combination occurring on each day.
    }
    \label{SEIR:fig:peak-incidence}
\end{figure}

>>>>

The majority of the confidence intervals contain the nominal probability (see \cref{SEIR:fig:sim-coverage}).
There is a tendency for the coverage to be slightly lower than the nominal probability, suggesting that the credible intervals are slightly too narrow; this is a common problem when using random-walk MCMC.
\todo{cite issues with random-walk MCMC exploring space}
This is similar when considering coverage of the derived quantities incidence and prevalence (see \cref{SEIR:fig:sim-inc-prev}).
\begin{figure}
    \includegraphics{SEIR/sim/coverage}
    \caption[Coverage of simulation study]{%
        Point estimate and 95\% confidence interval for coverage of the 50\%, 75\%, and 95\% central credible intervals for each parameter; see text for full definition.
        Vertical lines show the nominal coverage.
    }
    \label{SEIR:fig:sim-coverage}
\end{figure}
\begin{figure}
    \thisfloatpagestyle{empty}
    \vspace{-3cm}
    \makebox[\textwidth][c]{\includegraphics[width=0.9\paperwidth]{SEIR/sim/predictive_coverage}}
    \caption[Coverage of simulation study (derived quantities)]{%
        Point estimate and 95\% confidence interval for coverage of the 50\%, 75\%, and 95\% central credible intervals for incidence (top) and prevalence (bottom); see text for full definition.
        Horizontal lines show the nominal coverage.
    }
    \label{SEIR:fig:sim-inc-prev}
\end{figure}

@@

The 11--16 age group (roughly corresponding to compulsory secondary school education) is estimated to have the highest incidence (see \cref{SEIR:fig:incidence}).
Incidence is smooth within each week but shows discontinuities between weeks.
This is because the parameters within $\matr{\beta}(t)$ are constant within each week.
A constant $\matr{\beta}(t)$ leads to exponential growth over short time periods, once the initial dynamics have died out.
When the peak in incidence is estimated to occur varied by region, but due to this reason, is almost always on a Sunday (see \cref{SEIR:fig:peak-incidence}).
For Yorkshire, the peak is estimated to occur in late October.
For all other regions, it is estimated to occur in late December or Early January, the period during which severe social distancing measures were applied.
\begin{figure}
    \includegraphics{SEIR/CIS/incidence}
    \caption[Posterior estimates of incidence]{%
        Posterior estimates (95\% CrI) of incidence by region and age.
        See main text for discussion.
    }
    \label{SEIR:fig:incidence}
\end{figure}

% \begin{figure}
%     \includegraphics{SEIR/CIS/p_peak}
%     \caption[Posterior estimates of peak incidence timing]{%
%         Posterior probability of the peak incidence for each region and age combination occurring on each day.
%     }
%     \label{SEIR:fig:peak-incidence}
% \end{figure}
